Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-10-21 referee.tex
Revised response B

The 10 pc quoted above is a parameter called \texttt{StarClusterCombineRadius}, and controls whether newly formed star particles will be merged within a certain radius. Within our original simulation, this parameter was set to 10 pc, meaning that all stars younger than 10 kyr and within 10 pc of each other are merged into a single star particle.  The 10 kyr timescale originates from the approximate protostellar timescale when the ionizing luminosity is linearly increased to its ZAMS value. We chose a value of 10 pc because it corresponds to the approximate radius where H$_2$ formation allows the gas to cool from the halo's virial temperature (e.g. Yoshida et al. 2006).

To ensure that this value does not affect our results, we have run a suite of test simulations for a range of this parameter, namely from 0.625 pc, increasing by a factor of two up to the original 10 pc. The simulations are a 1 comoving Mpc$^3$ box with the same mass and spatial resolution and physics set, zoomed-in on a single halo with a mass of $10^{5.8} M_{\odot}$ at the end of the run. The simulations run for a total of 10 Myr after the first star forms. We see the same number of Pop III stars form regardless of the chosen value for the merging parameter. Thus, we conclude that our results are independent of this value. We have added these details to Section 2.2.1.

@@

A short description of Rockstar has been added in section 3.1, where Rockstar is introduced.

We have compared the mass calculations between Rockstar and Machacek+01 and have found that the masses are comparable. The difference between Rockstar halo masses and the Machacek+01 halo mass definition varies by a few percent. At high redshifts, when Pop III stars are forming, $\rho_c = \rho_m$, so our calculations are not affected by this difference, and allows the two mass definitions to be directly compared.

>>>>

The 10 pc quoted above is a parameter called \texttt{StarClusterCombineRadius}, and controls whether newly formed star particles will be merged within a certain radius. Within the presented simulation, this parameter was set to 10 pc, meaning that all stars younger than 10 kyr and within 10 pc of each other are merged into a single star particle.  The 10 kyr timescale originates from the approximate protostellar timescale when the ionizing luminosity is linearly increased to its ZAMS value. We chose a value of 10 pc because it corresponds to the approximate radius where H$_2$ formation allows the gas to cool from the halo's virial temperature (e.g. Yoshida et al. 2006).

To ensure that this value does not affect our results, we have run a set of simulations that tests the robustness of our results on this parameter.  Specifically, we have varied it from 0.625 pc to the original 10 pc, increasing the radius by a factor of two in each simulation. The simulations have the same boxsize of 1 comoving Mpc$^3$ with the same mass/spatial resolution and physics set, zoomed-in on a single halo with a mass of $10^{5.8} M_{\odot}$ that collapses at $z = 22$. We run the  simulations for a total of 10 Myr after the first star forms. We see the same number of Pop III star particles form regardless of the chosen value for the merging parameter. Thus, we conclude that our results are independent of this value. We have added these details to Section 2.2.1.

@@

We have added a short description of Rockstar to Section 3.1, where it is introduced.

We have also compared the mass calculations between Rockstar and Machacek et al. (2001) and have found that the masses are comparable. The difference between Rockstar halo masses and the Machacek et al. halo mass definition varies by a few percent. At very high redshifts when Pop III stars are forming, the mass density is equivalent to the critical density ($\rho_c = \rho_m$), so our calculations are not affected by this difference, and allows the two mass definitions to be directly compared.
